---
title: "HW4 Univariate Models"
output: html_document
name: Monica Connelly
date: February 1, 2018
---

# Read in Data
```{r}
tree_metadata <- 
treedata <- read.csv('https://raw.githubusercontent.com/dmcglinn/quant_methods/gh-pages/data/treedata.csv', header=T)
treedata_subset <- read.csv('https://raw.githubusercontent.com/dmcglinn/quant_methods/gh-pages/data/treedata_subset.csv', header=T)
library(car)

```


# Question 1
```{r}

trees_1abies <- treedata[treedata$species == "Abies fraseri", ]
trees_2acer <- treedata[treedata$species == "Acer rubrum", ]

pairs(trees_1abies, lower.panel = panel.smooth, upper.panel = NULL)

## fix to just be for one species and repeat
modspc1 <- lm(treedata$cover ~ treedata$species=="Abies fraseri")
modspc1

modspc2 <- lm(treedata$cover ~ treedata$species=="Acer rubrum")
modspc2

## fix models to assess more variables
modspc1b <- lm(trees_1abies$cover ~ trees_1abies$utme + trees_1abies$utmn + trees_1abies$utmn + trees_1abies$elev + trees_1abies$disturb + trees_1abies$streamdist + trees_1abies$tci)
modspc1b

modspc2b <- lm(trees_2acer$cover ~ trees_2acer$utme + trees_2acer$utmn + trees_2acer$elev + trees_2acer$disturb + trees_2acer$tci + trees_2acer$streamdist + trees_2acer$beers)
modspc2b

panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor=3, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y))
    txt <- format(c(r, 0.123456789), digits = digits)[1]
    txt <- paste0(prefix, txt)
    if(missing(cex.cor)) 
        cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor)
}

pairs(trees_2acer, lower.panel = panel.smooth, upper.panel = panel.cor)

pairs(trees_1abies, lower.panel = panel.smooth, upper.panel = panel.cor)

## run ANOVA here (I may need help with this function)
library(car)
anovaspc1 <- Anova(modspc1)
anovaspc1
anovaspc2 <- Anova(modspc2)
anovaspc2

```

## Additional Questions
1. How well does the exploratory model appear to explain cover?
  a) the model doesn't appear to explain the model very well, much of the data in the exploratory analysis appears to be clustered

2. Which exploratory variables are the most important?
  a) the standard deviations and correlation coefficients are the most important

3. Do model diagnostics indicate any problems with violations of OLS assumptions?
  a) yes, the OLS assumption of no multicolinearity appears to be violated

4. Are you able to explain variance in one species better than another?  Why might this be the case?
  a) Yes, the Abies species appears to be better explained becaue it doesn't violate as many OLS assumptions.


# Question 2
```{r}

acer_glm <- glm(trees_2acer$cover ~ trees_2acer$utme + trees_2acer$utmn + trees_2acer$elev + trees_2acer$tci + trees_2acer$streamdist + trees_2acer$disturb + trees_2acer$beers, 
                family='poisson')
acer_glm

abies_glm <- glm(cover ~ utme + trees_1abies$utmn + trees_1abies$elev + trees_1abies$tci + trees_1abies$streamdist + trees_1abies$disturb + trees_1abies$beers, data=trees_1abies,
                family='poisson')
abies_glm


abies_pseudo_r2 = function(abies_glm) {
     1 -  abies_glm$deviance / abies_glm$null.deviance
 }
abies_pseudo_r2

acer_pseudo_r2 <- function(acer_glm) {
    1 -  acer_glm$deviance / acer_glm$null.deviance
}
acer_pseudo_r2
```

## Additional Questions
1. Does it appear that changing the error distribution changed the results much?  In what ways?
  a) Yes, the pseudo r2 values altered, causing that for abies to be closer to 1 and that for acer to be farther from 1.


# Question 3
1. English summary of what I have found and what conclusions we can take away from my analysis?
  a) 


# Question 4 (optional)
```{r}

```


# Question 5 (optional)
```{r}

```

