---
title: "HW6 Spatial Models"
output: html_document
name: "Monica Connelly"
date: "February 15, 2018"
---

## Input Packages and Data
```{r}
data(BCI)
BCI_xy = data.frame(x = rep(seq(625754, 626654, by = 100), each=5),y = rep(seq(1011569, 1011969, by=100), len=50))
BCI_xy
BCI
```


## Question 1
Examine if there is evidence of spatial dependence in a rare and a common species in the BCI tree dataset.
```{r}
plot(BCI_xy)
colSums(BCI)
BCI_allsums = colSums(BCI)
BCI_allsums
quantile(BCI_allsums, c(.25, .75))

BCI_rare = BCI[ , BCI_allsums < 8]
BCI_rare

BCI_comm = BCI[ , BCI_allsums > 81]
BCI_comm

colnames(BCI_rare)

BCI_srlow = apply(BCI, 1, function(x) sum(x < 8))
hist(BCI_srlow)

BCI_srhigh = apply(BCI, 1, function(x) sum(x > 82))
hist(BCI_srhigh)

plot(BCI_xy, cex=BCI_allsums)


plot(BCI_allsums, cex = (BCI_allsums < 8))
plot(BCI_allsums)

vegdist(BCI_xy)
```

a. There is evidence of spatial dependence. more so on rare than on common speacies.


## Question 2
Build two generalized linear models to predict the abundance of the species Drypetes standleyi using the abundance of other tree species in the study site.
```{r}

sp_ids = c("Cordia.lasiocalyx", "Hirtella.triandra",
           "Picramnia.latifolia", "Quassia.amara",
           "Tabernaemontana.arborea", "Trattinnickia.aspera", 
           "Xylopia.macrantha")

sp_a = BCI[ , "Cordia.lasiocalyx"]
sp_b = BCI[ , "Hirtella.triandra"]
sp_c = BCI[ , "Picramnia.latifolia"]
sp_d = BCI[ , "Quassia.amara"]
sp_e = BCI[ , "Tabernaemontana.arborea"]
sp_f = BCI[ , "Trattinnickia.aspera"]
sp_g = BCI[ , "Xylopia.macrantha"]

BCI_short = cbind(sp_a, sp_b, sp_c, sp_d, sp_e, sp_f, sp_g)

head(BCI_short)

BCI_mod1 = 

BCI_mod2 = 

```


1) Did including the spatial error term have a large impact on the coefficients of the model?
  a. 

2) Did including the spatial error terms significantly improve model fit?
  a. including the exponential spatial error term made the model fit better

3) Explain why you did or did not observe a difference in the influence of adding the spatial error term between the two models.
  a. 


##Note
I understand what the lesson is getting at and what I should be seeing in the data, however the code to get to that point is stil confusing to me.  I am submitting this and will review the answer key as well as work with a classmate to attempt to understand the code.


