---
title: "HW6 Spatial Models"
output: html_document
name: "Monica Connelly"
date: "February 15, 2018"
---

## Input Packages and Data
```{r}
data(BCI)
BCI_xy = data.frame(x = rep(seq(625754, 626654, by = 100), each=5),y = rep(seq(1011569, 1011969, by=100), len=50))
BCI_xy
BCI
```


## Question 1
Examine if there is evidence of spatial dependence in a rare and a common species in the BCI tree dataset.
```{r}
plot(BCI_xy)
colSums(BCI)
BCI_allsums = colSums(BCI)
BCI_allsums
quantile(BCI_allsums, c(.25, .75))

BCI_rare = BCI[ , BCI_allsums < 8]
BCI_rare

BCI_comm = BCI[ , BCI_allsums > 81]
BCI_comm

colnames(BCI_rare)

BCI_srlow = apply(BCI, 1, function(x) sum(x < 8))
hist(BCI_srlow)

BCI_srhigh = apply(BCI, 1, function(x) sum(x > 82))
hist(BCI_srhigh)

plot(BCI_xy, cex=BCI_allsums)


plot(BCI_allsums, cex = (BCI_allsums < 8))
plot(BCI_allsums)

vegdist(BCI_)
```

a. There is evidence of spatial dependence. more so on rare than on common speacies.


## Question 2
Build two generalized linear models to predict the abundance of the species Drypetes standleyi using the abundance of other tree species in the study site.
```{r}




```


1) Did including the spatial error term have a large impact on the coefficients of the model?
  a. 

2) Did including the spatial error terms significantly improve model fit?
  a. 

3) Explain why you did or did not observe a difference in the influence of adding the spatial error term between the two models.
  a. 



